Impact of Context in the Perception of a Robot

### 2015-07-01 main.tex
Implemented Kshitij changes + rewritten discussion of results

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

@@

\abstract{
What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot and the design of its behaviours do obviously play a key
role. This paper however evidences another mechanism at play, more subtle and partially
unconscious: the context of the interaction, and more precisely, the cognitive
prerequisites that the interaction presupposes.

To study this effect, we propose an original methodology based on eye-tracking
and a set of stimuli that are visually identical and yet elicit different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.).
Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
as the \emph{anthropomorphic design} of the robot, and we call
\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
the (real or imagined) interaction between a non-human agent (a robot in our
case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots~\citep{lemaignan2014dynamics}, and we propose therefore that
anthropomorphism can be a useful \emph{proxy} to these intricate psychological
bonds. This article aims at advancing our understanding of this phenomenon
\textbf{by evidencing the impact of the cognitive presuppositions implied by the
context of the interaction}.

The study of context in HRI is not new. \textit{Context of use} is defined by
the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
and the physical and social environments in which a product is used''}, and
accordingly, there are various aspects that can impact how a robot is
experienced. The real or imagined \textit{purpose} of a robot, including the
application context in which it is typically used (\eg office environment, home,
rehabilitation center, public space, \etc) as well as the task context (\eg
serious or playful task; composition of human-robot team; number of users) and
the (social) role in which the robot is used / experienced are taken into
account. Generally, when the context of use of a robot is social, entertaining
or playful, it will enhance anthropomorphism, compared to when the context is a
routine or focused serious task (security, rescue, \etc).
\citet{joosse_what_2013} showed, for instance, that when the same robot ({\sc
nao}) was used in a different task context (cleaning task \vs tour guide), users
ascribed different personalities to the robot. \citet{goetz_cooperation_2002}
revealed a link between a robot's context of use and people's perception of the
robot: the authors found that people prefer a serious robot for serious tasks
and a less serious robot for more playful tasks. \citet{kaplan_free_2000}
discussed the role of uselessness in the design of robots. The author argues
that artificial pets like AIBO have no real purpose, in a sense that they do not
provide any kind of service or, in other words, \textit{``they are not doing
what you tell them to do''} and \textit{``they might refuse the order of its
owner''}. It may be this very aspect that increases people's tendency to
anthropomorphize the robot. According to Kaplan, it is in our daily use language
that we tend to attribute intentions to devices that are not doing their job
well.

@@

Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
discusses the effects of these changes and differentiates between what she calls
an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
robot, people might respond ``mindlessly'' instead of responding
consciously~\citep{nass_machines_2000}, and only after what is called the
\emph{familiarization} period, one might respond in a more reflective manner
instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
instance that subjects interacting with technologies in ways close to how they
would behave towards people, would deny any human-like interaction in a post-hoc
questionnaire, illustrating this reflective perspective.

@@

We take here a different approach to measure anthropomorphism, based on
eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
been able to evidence significantly different patterns in two experimental
conditions subtly different in terms of human-likeness. This eye-tracking based
metric is behavioural and hence does not suffer post-hoc reconstruction by the
subjects, possibly providing a better, ``noise-less'', access to the human
attitude towards the machine, and, as such, a better proxy to the cognitive and
affective bonds that the human establishes with the robot.

@@

Our first hypothesis \h{1} is then that gaze behaviour only is sufficient to
know if a subject is looking at a robot or at a human.  More precisely, we
hypothesize that the distribution of gaze fixations on the different body parts
is significantly different when watching a robot or a human performing the same
task.

Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
behaviours between the human and robot conditions correlates with the
participants' initial tendency to anthropomorphize, measured from a standard
pre-questionnaire: we expect that people with high tendency to anthropomorphize
will tend to have similar gaze behaviours while watching either a robot or a
human performing the same task.

@@

Finally, the hypothesis \h{4} examines whether the cognitive context affects the
general tendency to anthropomorphize, \ie whether observing a
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots (and vice versa).

@@

As hinted, this study is build as an eye-tracking experiment (using a stationary
eye-tracker) where participants watch short videos of an agent -- either a robot
(Aldebaran Robotics' Nao) or a human -- performing very simple task (picking an
object or pointing toward a sound source), in two different socio-cognitive
contexts.  These contexts, created by priming and/or audio cues, are designed to
elicit either a shallow cognitive context (that participant would refer as a
\emph{machine-like situation}) or a deeper cognitive context (refered as a
\emph{human-like situation}).

Besides eye-tracking, the participants' perception of robots is assessed through a
pre- and a post-questionnaire, described below.

@@

    \tikzmark{left}
    \begin{tabular}{l|p{2.5cm}|p{2.5cm}}
        & \tikzmark{top1} Shallow cognitive context & Deep cognitive \tikzmark{top2} context  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
            (top -| top1.west) --  (top -| top2.east) node[midway, above=0.5em] {\scriptsize between subjects};

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
            (left |- bottom) --  (left |- left1.north) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
    \end{tikzpicture}
    %%%

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Picking} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Sound} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Sound} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-noise}
    }

@@

Before starting the experiment, the participants were asked to fill a
pre-questionnaire which had 49 questions (5-point Likert scale). The
questionnaire comprised of questions assessing their familiarity for robots, 10
items from \emph{big-five} personality questionnaire, 15 questions taken from
Godspeed questionnaire (questions related to \emph{anthropomorphism},
\emph{likeability} and \emph{perceived intelligence}), 20 questions rating
human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
the pre- and post-questionnaires are available online:
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
typically took 5 minutes for participants to fill. The results were turned into
a score noted \anti (\emph{initial tendency to anthropomorphize}) following a
method presented below (section~\ref{questionnaires_processing}).

@@

\fxwarning{Was it first the pre-questionnaire or the familiarization?}
Before the experiment, participants were made to read, understand and sign a
consent form. Participants were then asked to fill the 49 questions of
the pre-questionnaire, without time constraint\fxwarning{right?}.

@@

\paragraph{Areas Of interest}

@@

We collected the gazes falling into one of these 10 zones and normalized them to
account for different total video duration and surface of AOIs between the robot
and human conditions\fxfatal{do we?}. We finally analyzed their distribution,
producing what we call \emph{gaze patterns}.

\paragraph{Difference in gaze patterns}

\fxfatal{To be rewritten} An important data to be obtained here is
$\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by taking the difference
between the ratio of net dwell time on an AOI and the AOI fixation coverage
summed over all the AOIs in the scene. Hence, $\delta_{\mathcal{H},\mathcal{R}}$
is expressed as a ratio in the range of 0 to 1. Similarly, the differences
between gaze patterns of two participants, where one watches the LC task, given
by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and the other watches the HC
task, given by $\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze
variables.

\subsubsection{Questionnaires processing}
\label{questionnaires_processing}
\fxnote{TDB}

@@

These values were computed by a direct sum of the rating provided by the
participants for the Godspeed's questions in the category
\emph{Anthropomorphism} and \emph{\fxwarning{?}...}. These ten questions were
rated between -2 and 2, hence \anti and \antf vary between -20 and 20.

The other questions (including the Big-Five personality test) were not used for
this study.

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{ManipulationCheck}
    \caption{\fxfatal{Incorrect nb of particpants! Label should be shallow/deep
    instead of low/high}Manipulation check}
    \label{fig:ManipulationCheck}
\end{figure}

@@

\subsection{Discussion}

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between human and robot interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the human scenario as
compared to the robot scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' \anti, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if \anti is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the robot videos are quite human-like for such participant.

The third hypothesis where we state that the gaze patterns can distinguish
between HC and LC tasks, can also be supported by our results. As can be seen in
figure 3(b), the proportion of time spent by participants on looking at the head
is significantly higher in HC task as compared to LC task. When participants
ascribe more anthropomorphic features to robot, they look more at the head than
when they ascribe less anthropomorphic features.

Finally for the fourth hypothesis where we state that the cognitive priming will
have an effect on \deltaant, as seen in the results, \deltaant
for participants that watched the HC task is greater than that for the
participants who watched LC task. This proves the fact that HLA was induced by
the videos and in fact, the HC tasks impose a greater HLA on the minds of
participants than the LC tasks. This shows the typical priming effect of the
audio command given in the beginning of the video and highlights the variation
in HLA based on the interaction scenario (LC versus HC) thereby supporting our
hypothesis.

We analyze the gaze distribution in this study only based on the AOI net dwell
times . Apart from this, the gaze transition among AOIs can be another way of
fetching gaze patterns which is not used in this study.

No correlation between delta opinion and gaze fixation on head: are we measuring
two different things? or hidden variable?

If different things, then, gaze is possibly a better metric: in-the-moment, does
not suffer post-hoc reconstruction.

@@

Our first contribution extends our understanding of the attribution of
human-like characteristics to robot by exploring the role of the interaction
context. As we show in the article, it appears that \textbf{even relatively
subtle context priming may lead to significantly different anthropomorphic
perceptions of the exact same robot, performing the exact same task}, as
confirmed both by distinct gaze patterns, and different reported perceptions in
questionnaires. As far as we know, this effect had not been previously
evidenced.

This leads to a second-order effect that we also evidence here: depending on the
cognitive context, the tendency to attribute human-like characteristics to robot
\textbf{evolves} in significantly different ways: after observing a robot in a
context that pre-suppose deeper cognitive capabilities, \textbf{people increase
their general tendency to anthropomorphize robots} compared to a shallow
cognitive context, even though the robot appearance and behaviour is the exact
same.

>>>>

\usepackage{tikz}
\usetikzlibrary{calc,decorations.pathreplacing}
\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

@@

\abstract{
What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot and the design of its behaviours do obviously play a key
role. This paper however reveals another mechanism at play, which is more subtle
and partially unconscious: the context of the interaction, and more precisely,
the cognitive prerequisites that the interaction presupposes.

To study this effect, we propose an original methodology based on eye-tracking
and a set of stimuli that are visually identical and yet induce different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.).
Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
as the \emph{anthropomorphic design} of the robot, and we call
\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
the (real or imagined) interaction between a non-human agent (a robot in our
case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots~\citep{lemaignan2014dynamics}. Therefore we propose therefore that
anthropomorphism can be a useful \emph{proxy} to these intricate psychological
bonds. This article aims at improving our understanding of this phenomenon
\textbf{by evidencing the impact of the cognitive presuppositions implied by the
context of the interaction}.

The study of context in HRI is not new. \textit{Context of use} is defined by
the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
and the physical and social environments in which a product is used''}.
Accordingly, there are various aspects that can impact how a robot is
experienced. The real or imagined \textit{purpose} of a robot, including the
application context in which it is typically used (\eg office environment, home,
rehabilitation center, public space, \etc) as well as the task context (\eg
serious or playful task; composition of human-robot team; number of users) and
the (social) role in which the robot is used / experienced are taken into
account. Generally, when the context of use of a robot is social, entertaining
or playful, it will enhance anthropomorphism compared to when the context is a
routine or focused serious task (security, rescue, \etc).
\citet{joosse_what_2013} showed, for instance, that when the same robot ({\sc
nao}) was used in a different task context (cleaning task \vs tour guide), users
ascribed different personalities to the robot. \citet{goetz_cooperation_2002}
revealed a link between a robot's context of use and people's perception of the
robot: the authors found that people prefer a serious robot for serious tasks
and a less serious robot for more playful tasks. \citet{kaplan_free_2000}
discussed the role of uselessness in the design of robots. The author argues
that artificial pets like AIBO have no real purpose, in a sense that they do not
provide any kind of service or, in other words, \textit{``they are not doing
what you tell them to do''} and \textit{``they might refuse the order of its
owner''}. It may be this very aspect that increases people's tendency to
anthropomorphize the robot. According to Kaplan, it is in our daily use language
that we tend to attribute intentions to devices that are not doing their job
well.

@@

Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
discusses the effects of these changes and differentiates between what she calls
an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation whereas a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
robot, people might respond ``mindlessly'' instead of responding
consciously~\citep{nass_machines_2000}, and only after what is called the
\emph{familiarization} period, one might respond in a more reflective manner
instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
instance that subjects interacting with technologies in ways close to how they
would behave towards people, would deny any human-like interaction in a post-hoc
questionnaire, illustrating this reflective perspective.

@@

We take here a different approach to measure anthropomorphism, based on
eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
been able to demonstrate significantly different patterns in two experimental
conditions subtly different in terms of human-likeness. This eye-tracking based
metric is behavioural and hence does not suffer post-hoc reconstruction by the
subjects, possibly providing a better, ``noise-less'', access to the human
attitude towards the machine, and, as such, a better proxy to the cognitive and
affective bonds that the human establishes with the robot.

@@

Our first hypothesis \h{1} is that gaze behaviour alone is sufficient to
know if a subject is looking at a robot or at a human.  More precisely, we
hypothesize that the distribution of gaze fixations on the different body parts
is significantly different when watching a robot or a human performing the same
task.

Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
behaviours between the human and robot conditions correlates with the
participants' initial tendency to anthropomorphize, measured from a standard
pre-questionnaire: we expect that people with high tendency to anthropomorphize
will tend to have smaller differences in their gaze behaviours while watching
either a robot or a human performing the same task.

@@

Finally, the hypothesis \h{4} examines whether the cognitive context affects the
general tendency to anthropomorphize, \ie whether observing a
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots (and vice versa). This also provides us
with a way to triangulate the behavioural measures with the subjective
attribution of anthropomorphism.

@@

As hinted, this study is build as an eye-tracking experiment (using a stationary
eye-tracker SMI RED 250) where participants watch short videos of an agent --
either a robot (Aldebaran Robotics' Nao) or a human -- performing very simple
task (picking an object or pointing toward a sound source), in two different
socio-cognitive contexts.  These contexts, created by priming and/or audio cues,
are designed to elicit either a shallow cognitive context (that participant
would refer as a \emph{machine-like situation}) or a deeper cognitive context
(refered as a \emph{human-like situation}).

Besides eye-tracking, the participants' perception of robots is assessed through a
pre- and a post-questionnaire interaction, described below.

@@

    \tikzmark{left}
    \begin{tabular}{l|p{4cm}|p{4cm}}
        & \tikzmark{top1} Shallow cognitive context & Deep cognitive context \tikzmark{top2}  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
        (top -| top1.west) --  (top -| bottom.east) node[midway, above=0.5em] {\scriptsize between subjects};

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
        ($(left |- bottom)+(1.8,-0.3)$) --  ($(left |- left1.north)+(1.8,0.2)$) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
    \end{tikzpicture}
    %%%

@@

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Picking} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-toys-anon}
    }

    \subfigure[\emph{Sound} task, robot condition]{
        \includegraphics[height=5cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Sound} task, human condition]{
        \includegraphics[height=5cm]{stimulus-human-noise-anon}
    }

@@

Before starting the experiment, the participants were asked to fill a
pre-questionnaire which had 49 questions (5-point Likert scale). The
questionnaire comprised of questions assessing their familiarity with robots, 10
items from \emph{Big-Five} personality questionnaire, 15 questions taken from
Godspeed questionnaire (questions related to \emph{anthropomorphism},
\emph{likeability} and \emph{perceived intelligence}) and 20 questions rating
human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
the pre- and post-questionnaires are available online:
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
typically took 5 minutes for participants to fill. The results were turned into
a score noted \anti (\emph{initial tendency to anthropomorphize}) following a
method presented below (section~\ref{questionnaires_processing}).

@@

Before the experiment, participants were made to read, understand and sign a
consent form. Participants were then asked to fill the 49 questions of
the pre-questionnaire, with a 10 minutes time limit that none of the participants
reached.

@@

\paragraph{Areas of interest}

@@

We collected the gazes falling into one of these 10 zones and normalized them to
account for different total video duration and surface of AOIs between the robot
and human conditions. We finally analyzed their distribution, producing what we
call \emph{gaze patterns}.

\paragraph{Differences between gaze behaviours}

To compare gazing behaviours across conditions, we compute a \emph{difference of
of gaze pattern} as...

\fxfatal{put here the formula + explanations}

\subsubsection{Questionnaires processing}
\label{questionnaires_processing}

@@

These values were computed by a direct sum of the rating provided by the
participants for the Godspeed's questions in the categories
\emph{anthropomorphism} and \emph{likeability}. These ten questions were rated
between -2 and 2, hence \anti and \antf vary between -20 and 20.  The other
questions (including the Big-Five personality test) were not used for this
study.

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{ManipulationCheck}
    \caption{Average ratings for the manipulation check question}
    \label{fig:ManipulationCheck}
\end{figure}

@@

\subsection{Discussion of the results}

The presented results bring some light on our initial hypotheses.

The clearly significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
proves that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive context was associated to a human-like situation (\h{0}).

The hypothesis \h{1} postulated that the gaze behaviours alone could tell if the
subjects was observing a robot or a human. Indeed, our results show
significantly different (normalized) fixations: the gaze distribution of a human
observer are different for humans and robots.

Hypothesis \h{2} looked at a possible interaction between our potential to
anthropomorphize (as measured in the pre-questionnaire) and our actual gaze
behaviour, the hypothesis being that high anthropomorphizers would show smaller
differences between the way they look at robots and humans (since they would
consider robots closer to humans than low anthropomorphizers). Our data supports
this hypothesis: participants reporting an higher tendency to anthropomorphize
tend to have similar gazing behaviours whether they look at humans or at robots.

To rephrase it: statistically speaking, your tendency to anthropomorphize things
is reflected in the way you look at these things: you will also look at them
\emph{as if they were humans}.

The third hypothesis \h{3} proposes that head fixations are related to the
cognitive context, which is clearly supported by our data: in deeper cognitive
context, one tends to spend more time looking at the head of the interacting
agent than in a shallow cognitive context. We also hypothesized that, in turn,
head fixations could act as a \emph{proxy to anthropomorphic projections}: as
underlined in the previous section, our data also support this second
hypothesis.

Finally, the hypothesis \h{4} looks at the dynamic of anthropomorphic
projections, with the hypothesis that watching an interaction with a particular
robot in a deeper cognitive context may impact \emph{globally} the
anthropomorphic perceptions of robots. This is supported by our study.

@@

Our first contribution extends our understanding of the attribution of
human-like characteristics to robot by exploring the role of the interaction
context. As we show in the article, it appears that \textbf{even relatively
subtle context priming may lead to significantly different anthropomorphic
perceptions of the exact same robot, performing the exact same task}, as
confirmed both by distinct gaze patterns, and different reported perceptions in
questionnaires. To the best of our knowledge, this effect had not been previously
evidenced.

This leads to a second-order effect that we also evidence here: depending on the
cognitive context, the tendency to attribute human-like characteristics to robot
\textbf{evolves} in significantly different ways: after observing a robot in a
context that pre-suppose deeper cognitive capabilities, \textbf{people increase
their general tendency to anthropomorphize robots} compared to a shallow
cognitive context, even though the robot appearance and visual behaviour is the
exact same.
